How to compute the fusion product of MV cycles in type A

### 2021-05-17 draft.tex

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$

@@

Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
% 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
and
% 
\begin{equation*}
    X(\tau')\ast_{\CC^\times} X(\tau'') = 
    \left\{
        (A,s)\in M_N(\CC) \times \CC^\times: 
        A \in X(\tau') \ast_s X(\tau'') 
    \right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

>>>>

We will need the following definitions.
\begin{definition}
Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
$$
\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
$$
% 
If $ \gamma \subset \{1, \dots, m\}$, we define
\begin{gather*}
    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
\end{gather*}
where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
\end{definition}

\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}

\begin{lemma}
    For any $ L \in \Grth$ and any $ 
    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
\end{lemma}
We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.

\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}

\begin{lemma} \label{le:Srdim}
    Let $ L \in \Grth$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in S_+^\mu$
        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
    \end{enumerate}
    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
\end{lemma}

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$
\acom{Need $L_{\{1,..,i\}}$ here.}

@@

Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
% 
\begin{equation*}
    \mathring X(\tau',\tau'')_{0,s} 
    % X(\tau')\ast_s \mathring X(\tau'') 
    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}
\end{equation*}
% 
and
% 
\begin{equation*}
    % X(\tau')\ast_{\CC^\times} X(\tau'') = 
    \mathring X(\tau',\tau'')_{0,\CC^\times} = 
    \left\{
        (A,s)\in M_N(\CC) \times \CC^\times: 
        A \in X(\tau') \ast_s X(\tau'') 
    \right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}
